Examination of shapes! (homework exam)

### 2016-02-29 geometricAlgorithms/homeworkExam/homeworkExam.tex
Improved the proof?

\paragraph{Proof} There are two cases to be proven:
	In case we can best horizontal cut a polygon $P$ into two equal areas
	we're done (since in this case there are no restrictions on the best
	horizontal cut line).
	In case we can't best horizontal cut polygon $P$ into two equal areas,
	the best horizontal cut has to minimise the larger area. In this case
	the best horizontal cut has to end on a vertex of $P$ according to
	the lemma. To prove this lets assume its not the case we end up of a
	vertex of $P$.
	However because the best horizontal cut has to minimize the larger
	area it will always end up on some sort of angle of the polygon, which
	is defined by a vertex and it can't equally divide the polygon because
	that was already handled
	by case one. So this shows that you end up with a contradiction.
	This is what had to be shown.

>>>>

\paragraph{Proof} There are two cases to be proven:
	In case we can best horizontal cut a polygon $P$ into two equal areas
	we're done (since in this case there are no restrictions on the best
	horizontal cut line).

	In case we can't best horizontal cut polygon $P$ into two equal areas,
	the best horizontal cut has to minimise the larger area. In this case
	the best horizontal cut has to end on a vertex of $P$ according to
	the lemma.

	To prove this lets assume its not the case a best horizontal cut's endpoint
	ends lies on a vertex of $P$ if dividing into two equal areas is impossible.
	However because the best horizontal cut has to minimize the larger
	area it will always end up on some sort of angle of the polygon, which
	is defined by a vertex. It can't equally divide the polygon because
	that was already handled by case one.
	So it can't be the case that the best horizontal cut does not
	end up on a vertex of $P$. This is what had to be shown.
